WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-07-09 ms.tex
Correct system for benchmark

Since \ac{BAYESTAR} is designed as one of the final steps in the real\nobreakdashes-time \ac{BNS} search, it is important to characterize how long it takes to calculate a sky map. We compiled \ac{BAYESTAR} with the Intel~C~Compiler~(\texttt{icc}) at the highest architecture\nobreakdashes-specific optimization setting (\texttt{-xhost}). We timed it under Scientific~Linux~6 on a Supermicro~1027GR\nobreakdashes-TRFT system with dual Intel Xeon E5-2670 CPUs clocked at 2.60GHz, providing a total of 16 cores and capable of executing 32 threads simultaneously (with hyperthreading). In Figure~\ref{fig:runtimes}, we show how long it took to calculate a localization with \ac{BAYESTAR} as the number of OpenMP threads was varied from 1 to 32. This is a violin plot, a smoothed vertical histogram. The magenta regions show run times for a two\nobreakdashes-detector network (HL) modeled on the first scheduled Advanced \ac{LIGO} observing run in 2015, and the blue regions show run times for a three\nobreakdashes-detector network (HLV) based on the second planned observing run in 2016. These are the two observing scenarios that are discussed in \cite{FirstTwoYears}.

@@

Several features are apparent. First, at any number of threads, the two configurations have similar run times, although the 2016 events contain a subpopulation of outliers that take about 2.5 times as long as the 2015 events. These are probably due to taking one of the more expensive code branches in the distance integral interpolation. Second, the run times decrease proportionally to the number of threads. A slight flattening at 32 threads may be due to increasing use of hyperthreading. Based on experiences running \ac{BAYESTAR} on the 32\nobreakdashes-core (64 threads with hyperthreading) cluster login machine, we expect the almost ideal parallel speedup to continue on machines with more threads.

>>>>

Since \ac{BAYESTAR} is designed as one of the final steps in the real\nobreakdashes-time \ac{BNS} search, it is important to characterize how long it takes to calculate a sky map. We compiled \ac{BAYESTAR} with the Intel~C~Compiler~(\texttt{icc}) at the highest architecture\nobreakdashes-specific optimization setting (\texttt{-ipo~-O3~-xhost}). We timed it under Scientific~Linux~6.1 on a Supermicro SuperServer 6028TP\nobreakdashes-HTTR system with dual 8\nobreakdashes-core Intel Xeon E5\nobreakdashes-2630~v3 CPUs clocked at 2.40\,GHz, capable of executing 32 threads simultaneously (with hyperthreading). In Figure~\ref{fig:runtimes}, we show how long it took to calculate a localization with \ac{BAYESTAR} as the number of OpenMP threads was varied from 1 to 32. This is a violin plot, a smoothed vertical histogram. The magenta regions show run times for a two\nobreakdashes-detector network (HL) modeled on the first scheduled Advanced \ac{LIGO} observing run in 2015, and the blue regions show run times for a three\nobreakdashes-detector network (HLV) based on the second planned observing run in 2016. These are the two observing scenarios that are discussed in \cite{FirstTwoYears}.

@@

Several features are apparent. First, at any number of threads, the two configurations have similar run times, although the 2016 events contain a subpopulation of outliers that take about 2.5 times as long as the 2015 events. These are probably due to taking one of the more expensive code branches in the distance integral interpolation. Second, the run times decrease proportionally to the number of threads. Based on experiences running \ac{BAYESTAR} on the 32\nobreakdashes-core (64 threads with hyperthreading) cluster login machine, we expect the almost ideal parallel speedup to continue on machines with even more processors.
